---
title: "Developing Data Product project"
author: "Amirhossein Vahidi"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: slidy_presentation
---
## Investigating the Fertility based on swiss dataset

```{r swiss, echo=FALSE}
head(swiss)
```
## Linear regression based on Agriculture 
- As you can see linear model can not show clear the correlation between fertility and percentage of male working agriculture

```{r library, include=FALSE}
library(plotly)
```
```{r plot1, echo=FALSE,message = FALSE,warning =FALSE}
data("swiss")
c<-plot_ly(data = swiss, x = ~ Agriculture, y = ~ Fertility, type = "scatter",mode ="markers" )
p<-add_trace(c, 
     x = swiss$Agriculture,
     y = fitted(lm(Fertility ~ Agriculture, swiss)),
     mode = "lines"
     )
p
```

## Linear regression based on Education
- education and fertility are correlated and with increasing the education thestandardize fertility is decreasing

```{r plot2, echo=FALSE,message = FALSE,warning =FALSE}
c<-plot_ly(data = swiss, x = ~ Education, y = ~ Fertility, type = "scatter",mode ="markers" )
p<-add_trace(c, 
     x = swiss$Education,
     y = fitted(lm(Fertility ~ Education, swiss)),
     mode = "lines"
     )
p
```

## Linear regression based on Catholic 
- There is a correlation between percenatge of catholics and fertility

```{r plot3, echo=FALSE,message = FALSE,warning =FALSE}
c<-plot_ly(data = swiss, x = ~ Catholic, y = ~ Fertility, type = "scatter",mode ="markers" )
p<-add_trace(c, 
     x = swiss$Catholic,
     y = fitted(lm(Fertility ~ Catholic, swiss)),
     mode = "lines"
     )
p
```

